### 2017-03-22 cone.tex
integrating cone constraint

\begin{theorem}
Let $\phi(s)$^\footnote{Here $\phi(s)$ is the $s^{th}$ row of the feature matrix $\Phi$} be the feature of the $s^{th}$ state. Let $i$ be a state whose constraints have not been retained and let $\{J}$ denote the set of states whose constraints have been retained. Further, let $\phi(i)\in \R^k$ lie in the linear span of vectors $\phi(j)\in \R^k,\forall j\in \J$, then
\begin{align}
(\Gamma J^*-\hg J^*)(i) \leq (\Gamma J^*-J^*)(i)+J^*(i)-\underset{j\in \J}{\sum} |\gamma_j| J^*(j)+ \underset{j\in \J}(|\gamma_j|-\gamma_j) B,
\end{align}
where $\gamma_j$ are the co-efficients of the linear span and $B\eqdef \underset{\underset{s\in S}{r\in \N}}{\max}(\Phi r) (s)$
\end{theorem}
\begin{proof}
Let $r^s_{\Gamma}$ and $r^s_{\hg}$ be such that $(\Phi r^s_{\Gamma})(s)=(\Gamma J^*)(s)$ and $(\Phi r^s_{\hg})(s)=(\hg J^*)(s)$
\begin{algin}
(\Gamma J^*-\hg J^*)(i) &=\phi(i) r^s_{\Gamma}- \phi(i) r^s_{\Gamma}
&=\phi(i) r^i_{\Gamma}- \underset{j\in \J}(|\gamma_j|+\gamma_j -|\gamma_j|)\phi(j) r^i_{\hg}
\leq \phi(i) r^i_{\Gamma}- \underset{j\in \J}|\gamma_j| J^*(j) + \underset{j\in \J} (|\gamma_j|-\gamma_j)B
= \phi(i) r^i_{\Gamma}- J^*(i)+ J^*(i) -\underset{j\in \J}|\gamma_j| J^*(j) + \underset{j\in \J} (|\gamma_j|-\gamma_j)B
\end{align}
\end{proof}

>>>>

%!TEX root =  autocontgrlp.tex
\begin{theorem}
Let $\phi(s)$%
\footnote{Here $\phi(s)$ is the $s^{th}$ row of the feature matrix $\Phi$} be the feature of the $s^{th}$ state. Let $i$ be a state whose constraints have not been retained and let $\{J\}$ denote the set of states whose constraints have been retained. Further, let $\phi(i)\in \R^k$ lie in the linear span of vectors $\phi(j)\in \R^k,\forall j\in \J$, then
\begin{align*}
\MoveEqLeft (\Gamma J^*-\hg J^*)(i)
 \leq 
(\Gamma J^*-J^*)(i) \\
& {}+J^*(i)-\underset{j\in \J}{\sum} |\gamma_j| J^*(j)
+ \underset{j\in \J}(|\gamma_j|-\gamma_j) B,
\end{align*}
where $\gamma_j$ are the co-efficients of the linear span and $B\eqdef \underset{\underset{s\in S}{r\in \N}}{\max}(\Phi r) (s)$
\end{theorem}
\begin{proof}
Let $r^s_{\Gamma}$ and $r^s_{\hg}$ be such that $(\Phi r^s_{\Gamma})(s)=(\Gamma J^*)(s)$ and $(\Phi r^s_{\hg})(s)=(\hg J^*)(s)$
\begin{align*}
\MoveEqLeft (\Gamma J^*-\hg J^*)(i) 
=\phi(i) r^s_{\Gamma}- \phi(i) r^s_{\Gamma}\\
&=\phi(i) r^i_{\Gamma}- \underset{j\in \J}(|\gamma_j|+\gamma_j -|\gamma_j|)\phi(j) r^i_{\hg}\\
&\leq \phi(i) r^i_{\Gamma}- \underset{j\in \J}|\gamma_j| J^*(j) + \underset{j\in \J} (|\gamma_j|-\gamma_j)B\\
&= \phi(i) r^i_{\Gamma}- J^*(i)+ J^*(i) -\underset{j\in \J}|\gamma_j| J^*(j) \\
& \quad + \underset{j\in \J} (|\gamma_j|-\gamma_j)B\,.
\end{align*}
\end{proof}

### 2017-03-22 grlp.tex
integrating cone constraint

Now, let $\phi_1,\ldots,\phi_k : \S \to \R$ be $k$ basis functions. 
\todoc{I think we should use $d$ to denote the number of basis functions. Or at least $n$. Low priority.} 
The \emph{Approximate Linear Program} (ALP) of \citet{SchSei85} 
is obtained by adding the linear constraints $J = \sum_{i=1}^k r_i \phi_i$ to the above linear program. Eliminating $J$ then gives $\min\{ \sum_i r_i c^\top \phi_i \,:\, \sum_i r_i \phi_i \ge g_a + \alpha \sum_i r_i P_a \phi_i, a\in \A, r = (r_i)\in \R^k \}$.
As noted by \citet{SchSei85}, the linear program is feasible as long as $\one$, defined as the vector with all components being identically equal to one, is in the span of $\{\phi_1,\dots,\phi_k\}$. 
\emph{For the purpose of computations, it is assumed that the values $c^\top \phi_i$, $i=1,\dots, k$ and the values $(P_a \phi_i)(s)$ and $g_a(s)$ can be accessed in constant time.} 
This assumption can be relaxed to assuming that one can access $g_a(s)$ and $\phi_i(s)$ for any $(s,a)$ in constant time, as well as to that one can efficiently sample from $c$, from $P_a(s,\cdot)$ for any $(s,a)$ pair, 
but the details of this are the beyond the scope of the present work. As shown by \citet{ALP}, if $\ralp$ denotes the solution to the above ALP then for $\Jalp \doteq \sum_i \ralp(i) \phi_i \doteq \Phi r$ it holds that $\norm{\Jalp - J^*}_{1,c} \le \frac{2 \epsilon}{1-\alpha}$ where $\epsilon = \inf_r \norm{ J^* - \Phi r }_\infty$ is the error of approximating the optimal value with the span of the basis functions $\phi_1,\dots,\phi_k$ and $\norm{J}_\infty = \max_s |J(s)|$ is the maximum norm.

>>>>

Now, let $\phi_1,\ldots,\phi_k : \S \to \R$ be $k$ basis functions. 
\todoc{I think we should use $d$ to denote the number of basis functions. Or at least $n$. Low priority.} 
The \emph{Approximate Linear Program} (ALP) of \citet{SchSei85} 
is obtained by adding the linear constraints $J = \sum_{i=1}^k r_i \phi_i$ to the above linear program. Eliminating $J$ then gives $\min\{ \sum_i r_i c^\top \phi_i \,:\, \sum_i r_i \phi_i \ge g_a + \alpha \sum_i r_i P_a \phi_i, a\in \A, r = (r_i)\in \R^k \}$.
As noted by \citet{SchSei85}, the linear program is feasible as long as $\one$, defined as the vector with all components being identically equal to one, is in the span of $\{\phi_1,\dots,\phi_k\}$. 
\emph{For the purpose of computations, it is assumed that the values $c^\top \phi_i$, $i=1,\dots, k$ and the values $(P_a \phi_i)(s)$ and $g_a(s)$ can be accessed in constant time.} 
This assumption can be relaxed to assuming that one can access $g_a(s)$ and $\phi_i(s)$ for any $(s,a)$ in constant time, as well as to that one can efficiently sample from $c$, from $P_a(s,\cdot)$ for any $(s,a)$ pair, 
but the details of this are the beyond the scope of the present work. As shown by \citet{ALP}, if $\ralp$ denotes the solution to the above ALP then for $\Jalp \doteq \sum_i \ralp(i) \phi_i \doteq \Phi r$ it holds that $\norm{\Jalp - J^*}_{1,c} \le \frac{2 \epsilon}{1-\alpha}$ where $\epsilon = \inf_r \norm{ J^* - \Phi r }_\infty$ is the error of approximating the optimal value with the span of the basis functions $\phi_1,\dots,\phi_k$ and $\norm{J}_\infty = \max_s |J(s)|$ is the maximum norm and $\Phi \in \R^{S\times k}$ is the matrix formed by $(\phi_1,\dots,\phi_k)$.
